### 2021-03-09 paper.Rmd
added bullet points for brushing and linking from "ggobi"
-code for figure of radial manual tour. -fix other space issue in \mathbb -NS TODO: add fig caption and w/h, and write up

To define whether a projection is interesting or not in the guided tour, an index function is used. An index function defines a surjection function from the projection $Y$ in $ \mathbb{R}^{n \times d}$ to a scalar in $\mathbb{R}$. For the high-dimensional data, an interesting projection is the one that deviates from normality, as discussed in @Diaconis1984-mv and @Huber1985-zq [expand more here]. Numerous index functions have been developed since the initial index proposed by @Friedman1974-ck: <!-- entropy-based index? --> holes and central mass index [@Cook2008-nl] computes the deviation of the projected data from a normal distribution; @Posse1995-ih proposed a chi-square index for detecting the spiral structure in the data;  kurtosis and skewness indices are raised in @Loperfido2020-xj and @Loperfido2018-ga to detect outliers in financial time series; and most recently, scagnostic indices [@Laa2020-zj] provides eight measures for summarising information between pairs of variables in scatter plot matrices.

@@

> something from nick's paper
> figure 9 illustration

@@

> something from ggobi book
> > figure 10: plots showing example

>>>>

To define whether a projection is interesting or not in the guided tour, an index function is used. An index function defines a surjection function from the projection $Y$ in $\mathbb{R}^{n \times d}$ to a scalar in $\mathbb{R}$. For the high-dimensional data, an interesting projection is the one that deviates from normality, as discussed in @Diaconis1984-mv and @Huber1985-zq [expand more here]. Numerous index functions have been developed since the initial index proposed by @Friedman1974-ck: <!-- entropy-based index? --> holes and central mass index [@Cook2008-nl] computes the deviation of the projected data from a normal distribution; @Posse1995-ih proposed a chi-square index for detecting the spiral structure in the data;  kurtosis and skewness indices are raised in @Loperfido2020-xj and @Loperfido2018-ga to detect outliers in financial time series; and most recently, scagnostic indices [@Laa2020-zj] provides eight measures for summarising information between pairs of variables in scatter plot matrices.

@@

> something from nick's paper.
> NS: something like figure 3, exlpaining radial tour on lda.
> figure 9 illustration

```{r}
##TODO, need to make caption, tag, and optimize figure width/height
source("./R/make_radial_tour_fig.r")
make_radial_tour_fig()
```

@@

> something from ggobi book
* Brushing as database query
* Brushing as conditioning
* Brushing as geometric sectioning
* Persistent vs. transient 
> > figure 10: plots showing example
